The importance of measurement uncertainty in ecological management

### 2018-01-26 manuscripts/manuscript.Rmd
WIP

# Model

We consider the management problem of setting catch quotas for a marine fishery in the face of imperfect information about the current stock size and uncertainty about future recruitment.  To facilitate tractability and intepretation, we will focus on the well-studied Gordon-Schaefer model [@Schaefer1954; @Gordon1954] of logistic population growth (stock recruitment),

$x_{t+1} = x_t r  \left(1 - \frac{x_t}{K}\right) - h_t \varepsilon_t$

where $x_t$ is the current stock size, $h_t$ the harvest chosen that year, with parameters $r$ giving the individual growth rate, and $K$ the carrying capacity and $\varepsilon$ representing stochastic recruitment in a variable environment.  We will assume for simplicity $\varepsilon \sim \mathcal{N}(1, \sigma_g)$.

This and similar models are widely used in large scale analyses across diverse stocks (e.g. [@Costello2016; @Britten2017]), and form the basis for much of bioeconomic theory [@Clark1990]. As such, it will be easier to compare our results against intuition and classic theory, and avoid the possibility of differences arsing only because of some particular subtle assumption hidden in a more complex model.

@@

@@

@@

# Current theory and practice

@@

This *constant yield* (constant mortality) solution thus corresponds to an equlibrium analysis, and does not solve the time-dependent optimization problem above. In particular, maximum sustainable yield will not be optimal whenever the stock is away from $B_{MSY}$.  @Clark1973 shows that the optimal time-dependent strategy is not one of constant yield, but rather of *constant escapement*. The time-depednent optimal stategy is impatient: it seeks to achieve the optimal yield as quickly as possible.  Thus, at any level below $B_{MSY}$, the economically optimal thing to do is to completely shut down the fishery, while above this stock, mortalities greater than $F_{MSY}$ can be optimal to bring the stock back to $B_{MSY}$ more quickly.  (This intution must be adjusted slightly in the case of economic discounting of future profits, but is otherwise quite general, see @Clark1990).  This strategy is known as constant escapement, since a constant sock size $B_{MSY}$ escapes harvest each year.  While both converge to the same long-term biomass and long-term yield, these differences away from equilibrium between the mortality-based approach that dominates fisheries management practice and the escapement-based approach that became the focus of theory will result in different behaviors under uncertainty.

<!-- Should TAC go here? -->

The literature of optimal harvests under uncertainty is one of paradoxes, which can only be resolved by a more comprehensive treatment of measurement uncertainty.

@@

The first of these we shall refer to as Reed's Paradox, owing to the mathematical proof provided in @Reed1979 which demonstrates that, under sufficiently general assumptions, the optimal escapement $S$ for a population under stochastic growth, is identical to the optimal escapement $D$ of a deterministic population, $S = D = B_{MSY}$.  This suprising result suggests that in going from a world where a manager has perfect knowledge of absolutely everything into a scenario where the manager faces considerable uncertainty about the future state of the world, no additional precaution is needed.  This also provides the manager with a remarkably convenient mechanism for determining the optimal harvest policy: rather than rely on computationally intensive Stochastic Dynamic Programming to determine the optimal policy, a simple derivative will suffice, which is all that is needed to solve the maximum of the deterministic problem.

@@

By leveraging algorithms (and also computational hardware) developed over two decades later are we able to crack this mathematical difficulty Clark refers to directly without this "simplyfying assumption."  Unforunately for @Clark1986, this "simplifying assumption" they made instead only deepened the paradox, leading them to find policies that become *less* cautious as uncertainty increases:

@@

Using a different but still flawed assumption nearly two decades later, @Sethi2005 largely confirm Clark's Paradox, which they likewise observed with some concern:

@@

While other attempts to introduce measurement error have been considered, each relies on various approximations that similarly alter the problem, such as assuming the solution must be of 'constant-escapement' type [@Ludwig1981; @Roughgarden1996; @Engen1997;  @Moxnes2003].  Here we will illustrate the use of powerful modern algorithms that will permit a more direct solution to the case of measurement uncertainty.  In addition to resolving this paradox, we will demonstrate this direct solution also out-performs current more heuristic rules of thumb such as those currently used in fisheries management to account for uncertainty.

## Uncertainty in Practice: TAC

Fortunately, management practice has so far ignored this paradoxical suggestion that uncertainty should be met with greater rather than reduced fishing quotas. Maximum Sustainable Yield (MSY) remains the basis of international law (including the UN,  IWC, IATTC, ICCAT, ICNAF; @Mace2001) and a familiar standard of management in terrestrial ecosystems as well as aquatic [@Clark1990].  Critics have for some time observed the limitations of harvesting at MSY in face of uncertainty in stock sizes and population dynamics [@Larkin1977; @Botsford1997].  Many US fisheries reflect this uncertainty through a series of adjustments that effectively reduce the target fishing mortality level to reflect this uncertainty.  Typically, a stock assessment model provides a best estimate of $B_{MSY}$ and corresponding mortality $F_{MSY}$ is used to define the stock Overfishing Limit, (OFL). Based on this, a somewhat lower level is set as the Allowable Biological Catch (ABC), reflecting uncertainty in the stock assessment. To reflect possible uncertainty between reported and actual catch, the ABC is reduced somewhat further to define the Total Allowable Catch, (TAC), which forms the basic unit of management for many such fisheries.  To reflect this process, our analysis will also consider policies in which the harvest quota is set at 80% of the level expected under and MSY policy: $H_{TAC}(t) = 0.8 \cdot F_{MSY} \cdot B_t$, for a biomass estimated at $B(t)$ in year $t$. To distinguish this approach from MSY, we will refer to this approach as a TAC policy.  This more closely represents a heuristic [e.g. @Hilborn2010] or resilience-based approach [sensu @Fischer2009] than an optimization-based policy.  Importantly, this approach shares the fundamentally stationary assumptions of an MSY policy by defining a constant mortality rather than a dynamic policy.  Thus, despite being more cautious overall and generating lower economic yield than a constant escapement policy, TAC policies continue to harvest at non-zero rates even if a stock falls below $B_{MSY}$, while the constant escapement policy does not.

@@

```{r sims, fig.width=7, fig.height=3.5, fig.cap="Average fish biomass under different management strategies under increasing levels of measurement uncertainty. Each plot the mean stock size over time across 100 replicate simulations under each policy: constant escapement (CE), Total allowable catch (TAC = 80% MSY), and the proposed partially observed Markov decision process (POMDP) method. Measurement error increases as a normal distribution with standard deviation 0, 0.1, or 0.15, as indicated at the top of the panel.  Environmental stochasticity is fixed a standard deviation of 0.15 in each panel.  Carrying capacity K normalized to 1, r = 0.75. Additional environmental noise levels and comparison to MSY rather than TAC can be found in the supplementary material. \\label{sims}"}
sims %>%
  select(-value) %>%
  filter(method != "msy", sigma_g == "0.15") %>%
  mutate(method = fct_recode(method, 
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  group_by(time, method, sigma_m) %>%
  summarise(mean = mean(state), sd = sd(state)) %>% 
  mutate(sigma_m = as.character(sigma_m)) ->
fig1_df

@@

```{r econ, fig.width=7, fig.height=3.5, fig.cap="\\label{econ}"}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g == "0.15", method != "msy") %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%
  mutate(method = fct_recode(method,
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%

@@

This pattern in management success in ecological terms (the relatively recovery and maintenance of fish biomass) is also bourne out in terms of economic performance.  Figure \ref{econ} shows the mean net present value (averaging across replicates and discounting future profits by the discount factor $\gamma$) for these same simulations at increasing levels of measurement uncertainty.  As before, environmental stochasticity is set at $\sigma_g = 0.15$.  In the absense of measurement uncertainty, constant escapement (CE) is optimal, though POMDP performs nearly as well, while TAC underperforms.  As measurement uncertainty increases, the economic value of CE declines, remaining better than TAC at modest measurement error $\sigma_m = 0.1$ but worse at higher uncertainty.  Though the risk of stock collapse does increase with increasing measurement error under TAC (as seen by the mean declines in Figure \ref{sims}), these have little impact on the economic value due to the discount rate.  A smaller discount rate would penalize unlikely but not improbable collapses more, since a significant amount of time is required to realize those rare events.  Supplemental Figure S3 summarizes these economic trends across different noise values $\sigma_g$ and includes comparison to a simple MSY policy.

@@

```{r overest, fig.width=4, fig.height=3.5, fig.cap = "\\label{overest}"}
overest_sims %>%
  filter(method != "MSY") %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1)) 
```

Figure \ref{overest} summarizes the results of the same simulations under the scenario in which the POMDP approach assumes a measurement error of $\sigma_m = 0.15$, when in fact all simulated measurements are made without error ($\sigma_m = 0$).  This represents an extreme case of ovestimating the measurement error. Stochastic growth remains the same as before, $\sigma_g = 0.15$, and simulations under TAC and CE policies are shown for comparison.  When measurement error is absent, Reed's proofs hold that the CE solution is optimal -- interestingly, the POMDP solutions track almost exactly the CE solution despite the misplaced assumption that measurements are quite poor.  As we have already seen, TAC solution is insufficiently cautious for this level of stochasticicty in recruitment, resulting in overexploitation and long-term decline. The ability of the POMDP solution to perform nearly optimally even when significantly overestimating the level of measurement uncertainty contrasts sharply to the significant declines from ignoring measurement uncertatinty seen in the CE solutions in Figure \ref{sim}.  This demonstrates that while we may not know precisely the level of measurement error, we achieve far better outcomes overestimating measurement uncertainty than underestimating it.  This also underscores the observation that POMDP policy is quite robust to the details of the uncertainty.  We can get a better understanding for the performance of POMDP in these simulations by looking more closely at how any individual decision under a POMDP strategy compares to the action chosen by the current alternatives.

```{r policy, fig.width=5, fig.height=7, fig.cap="\\label{policy}", message=FALSE, warning=FALSE}
policies_w_priors %>% 
  gather(panel, value, -state, -policy) %>%
  ggplot(aes(state, value, col=policy)) + 
  geom_line(lwd=1)  +
  facet_wrap(~panel, ncol=1, scales = "free_y") +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0,.8)) + 
  theme(legend.position = "bottom")
```

To better understand the differences in performance of these strategies and resolve the paradox of uncertainty, we must take a closer look at how the specific action recommended by each policy compares given the same observation.  Figure \ref{policy} shows the action taken by each strategy in response to a measurement of the stock size.  The first panel shows the policy in terms of expected escapement, $S = Y - H$ for observed stock $Y$ and harvest $H$, consistent with most of the relevant control and bioeconomics literature [e.g. @Reed1979; @Clark1986; @Sethi2005].  For comparison, the second panel shows the same policies but in terms of harvest $H$.  These plots clearly illustrate the contrast between the constant escapement (CE) strategy and the precautionary Total Allowable Catch (TAC) strategy: CE sets harvest strictly to zero for stocks estimated at biomass below $B_{MSY}$, while TAC permits a modest harvest of even very small stocks.  Viewing the same policies in terms of escapement, makes it clear that only CE strategy corresponds to keeping escapement constant.  This is important, as theoretical work ever since the proofs of @Reed1979 often attempts to simplify the calculations by assuming the optimal policy must be a constant-escapement type strategy [e.g. @Ludwig1981; @Roughgarden1996; @Engen1997;  @Moxnes2003].  Note that both CE and TAC policies are independent of the levels of uncertainty $\sigma_m$ and $\sigma_g$.  TAC implicitly accounts for some uncertainty through its 80% MSY definition -- comparable plots with MSY can be found in the Supplemental Material.  In principle, the CE policy could depend on $\sigma_g$, but as @Reed1979 proved, the constant escapement level with stochasticity is the same as in the deterministic case, S = D, unless the noise level is quite high (comparison plots in Supplemental material.)  In contrast to this, our POMDP plots depend very much on both the choice of $\sigma_m$ and $\sigma_g$.  If $\sigma_m = 0$, they reduce exactly to the CE solution.  Here we show the corresponding policies for POMDP solutions focusing on $\sigma_g = 0.15$ as above, with a modest measurement uncertainty $\sigma_m = 0.1$.  Alternate combinations of measurement uncertainty can be found in the appendix but do not change the general pattern.  In addition to an explicit dependence on the measurement error, our POMDP solutions depend on another piece of information: any prior observations of the stock size.

@@

So far we have focused on simulation and an examination of the relative policies under different prior information.  Figure \ref{histroical} compares the harvest level that would have been recommmended by each of the strategies we have considered here against the historically observed catch recorded for two commericially fished stocks: Argentine Hake and European Plaice.  Historical estimates of biomass and catch are taken from the R.A. Myers Legacy Stock Assessment database [@RAM]. Posterior distributions for parameters for the Graham-Schaefer model are estimated with uncertainty through Markov Chain Monte Carlo using `nimble` [@nimble] on the historical data, illustrating how this process might be done in more complex models as well (details and code in Supplement, Appendix B).  $B_{MSY} and corresponding TAC and CE policies are calculated based on posterior mean estimates of the model parameters, along with POMDP solution assuming a 10% measurement error rate.  Though measurement error could be estimated directly from the raw data, this would not reflect the true measurement uncertainty arising from the stock assessment process.  Each strategy is then compared to historical observations to determine a recommended harvest.  As we have seen, the TAC and CE harvest policies are uniquely determined by the observed stock size relative to $B_{MSY}$, but the POMDP policy must be re-calculated each time step to reflect both the prior observation and prior action.  Note that since we cannot replay history under these alternative policies, so the prior action taken is always the historical catch for that year and not the catch recommended by the POMDP policy.

These historical examples provide another useful lens to compare how the different strategies respond in the face of fluctuations in real data, rather than model simulations.  In both stocks, historical catch almost always exceeds that recommended by any of our strategies, falling closer to the MSY value estimated (see appendix).   In Argentine Hake, the persistent declines result in both POMDP and CE strategies quicly closing down the fishery in an attempt to let the stock recover to a more productive target biomass, while TAC persists with merely a reduced harvest.  A small recovery of biomass in 1995 is met by an immediate uptick in harvest under CE, while the POMDP response is more conservative.  The example of European Plaice illustrates more volatility in the stock size, revealing further differences in the strategies.  Despite this volatility, the TAC level remains relatively level across all five decades, rising or dipping only slightly with changes in stock size.  In contrast, the CE harvest tracks this volatility almost in perfect mirror.  Here, the POMDP solution falls in between these extremes, almost mirroring which-ever of the two policies is more conservative: the POMDP solution matches the dips in harvest taken by CE to allow the stock to recover most quickly, but does not track the doubling of harvests recommended by CE in the mid 1980, increasingly only to the more modest harvest recommended by the TAC policy.

Once again, we see that POMDP solution provides a more consistently precautionary policy than either the over-simplified optimal control solution of CE or the more rule-of-thumb approach represented by TAC.  Though we have seen that the POMDP solution need not always be more conservative (lower harvest) than these strategies, it makes use of the all prior observations to tune the level of caution appropriately.

## Discussion

Using modern algorithms we have been able to crack the nut of measurement uncertainty in the optimal management of marine fisheries and debunk a long-standing paradox that increased measurement uncertainty should be met with larger harvests.  We have illustrated that the POMDP approach introduced here performs consistently better across a range of stochastic growth and measurement error levels, while previous solutions based on either classic optimal control solutions or heuristic rules-of-thumb give significantly worse outcomes in both ecological and economic terms.  Nevertheless, it may be tempting to see these results as either trivial or impractical, but a closer inspection reveals they are neither.

>>>>

@@

We consider the management problem of setting catch quotas for a marine fishery in the face of imperfect information about the current stock size and uncertainty about future recruitment.

@@

## Population model

To facilitate tractability and intepretation, we will focus on the well-studied Gordon-Schaefer model [@Schaefer1954; @Gordon1954] of logistic population growth (stock recruitment),

$$x_{t+1} = x_t r  \left(1 - \frac{x_t}{K}\right) - h_t \varepsilon_t$$

where $x_t$ is the current stock size, $h_t$ the harvest chosen that year, with parameters $r$ giving the individual growth rate, and $K$ the carrying capacity and $\varepsilon$ representing stochastic recruitment in a variable environment.  We will assume for simplicity $\varepsilon \sim \mathcal{N}(1, \sigma_g)$.  This and similar models are widely used in large scale analyses across diverse stocks (e.g. [@Costello2016; @Britten2017]), and form the basis for much of bioeconomic theory [@Clark1990]. As such, it will be easier to compare our results against intuition and classic theory, and avoid the possibility of differences arsing only because of some particular subtle assumption hidden in a more complex model.

@@

# Current Theory and Practice

@@

This *constant yield* (constant mortality) solution thus corresponds to an equlibrium analysis which does not solve the time-dependent optimization problem above. In particular, this maximum sustainable yield (MSY) strategy will not be optimal whenever the stock is away from $B_{MSY}$.  @Clark1973 deomonstrated (assuming no uncertainty in measurement or stochasticity in population dynamics) that the optimal time-dependent strategy is not one of constant yield, but rather of *constant escapement*. We will return to this approach in a moment.

## Uncertainty in Practice: MSY & TAC

Maximum Sustainable Yield (MSY) remains the basis of international law (including the UN,  IWC, IATTC, ICCAT, ICNAF; @Mace2001) and a familiar standard of management in terrestrial ecosystems as well as aquatic [@Clark1990].  Critics have for some time observed the limitations of harvesting at MSY in face of uncertainty in stock sizes and population dynamics [@Larkin1977; @Botsford1997].  Many US fisheries reflect this uncertainty through a series of adjustments that effectively reduce the target fishing mortality level to reflect this uncertainty.  Typically, a stock assessment model provides a best estimate of $B_{MSY}$ and corresponding mortality $F_{MSY}$ is used to define the stock Overfishing Limit, (OFL). Based on this, a somewhat lower level is set as the Allowable Biological Catch (ABC), reflecting uncertainty in the stock assessment. To reflect possible uncertainty between reported and actual catch, the ABC is reduced somewhat further to define the Total Allowable Catch, (TAC), which forms the basic unit of management for many such fisheries.  To reflect this process, our analysis will also consider policies in which the harvest quota is set at 80% of the level expected under and MSY policy: $H_{TAC}(t) = 0.8 \cdot F_{MSY} \cdot B_t$, for a biomass estimated at $B(t)$ in year $t$. To distinguish this approach from MSY, we will refer to this approach as a TAC policy.  This more closely represents a heuristic [e.g. @Hilborn2010] or resilience-based approach [sensu @Fischer2009] than an optimization-based policy.  Importantly, this approach shares the fundamentally stationary assumptions of an MSY policy by defining a constant mortality rather than a dynamic policy.  Thus, despite being more cautious overall and generating lower economic yield than a constant escapement policy, TAC policies continue to harvest at non-zero rates even if a stock falls below $B_{MSY}$, while the constant escapement policy does not.

## Optimal management

So far, attempts to provide a more formal basis for managing uncertainty than the heuristic adjustment of catch limits described above have largely foundered in a series of of paradoxes.  Without uncertainty, the theoretical policies are quite intuitive: The result derived by @Clark1973 for an optimal dynamic strategy to replace the equilibrium solution of MSY can be summarized as: If the stock is most productive at $B_{MSY}$, then obtain $B_{MSY}$ as quickly as possible. Thus, at any level below $B_{MSY}$, the economically optimal thing to do is to completely shut down the fishery, while above this stock, harvests greater than $H_{MSY}$ will be needed to bring the stock back to $B_{MSY}$.  (This intution must be adjusted slightly in the case of economic discounting of future profits, but is otherwise quite general, see @Clark1990).  This strategy is known as constant escapement, since a constant sock size $B_{MSY}$ escapes harvest each year.  While both converge to the same long-term biomass and long-term yield, these differences away from equilibrium between the mortality-based approach that dominates fisheries management practice and the escapement-based approach that became the focus of theory will result in different behaviors under uncertainty.  Intuitively, any uncertainty, either in the population growth model (stochasticity), or measurement error, should seem to justify harvesting fewer fish, as is built into the TAC limits discussed above. Yet formal treatments of these issues have so far required approximations, and these approximations have driven paradoxical conclusions which we briefly summarise here.

@@

The first of these we shall refer to as Reed's Paradox for stochastic growth, owing to the mathematical proof provided in @Reed1979 which demonstrates that, under sufficiently general assumptions, the optimal escapement $S$ for a population under stochastic growth, is identical to the optimal escapement $D$ of a deterministic population, $S = D = B_{MSY}$.  This suprising result suggests that in going from a world where a manager has perfect knowledge of absolutely everything into a scenario where the manager faces considerable uncertainty about the future state of the world, no additional precaution is needed.  This also provides the manager with a remarkably convenient mechanism for determining the optimal harvest policy: rather than rely on computationally intensive Stochastic Dynamic Programming to determine the optimal policy, a simple derivative will suffice, which is all that is needed to solve the maximum of the deterministic problem.

@@

Unforunately for @Clark1986, this "simplifying assumption" serves to squash most of the measurement error, and their results instead only deepened the paradox, finding policies that become even *less* cautious as uncertainty increases:

@@

Relying on a quite different but still flawed assumption nearly two decades later, @Sethi2005 largely confirm Clark's Paradox, which they likewise observed with some concern:

@@

Despite these notes of caution, both @Clark1986 and @Sethi2005 ultimately attempt to rationalize this counter-intuitive conclusion rather than rejct it.  Others have also attempted to introduce measurement error, but always relying on various approximations that similarly alter the problem. The most common such assumption is to assume from the outset that the solution must be of 'constant-escapement' type [@Ludwig1981; @Roughgarden1996; @Engen1997;  @Moxnes2003].  Here we will illustrate the use of powerful modern algorithms that will permit a more direct solution to the case of measurement uncertainty.  In addition to resolving this paradox, we will demonstrate this direct solution also out-performs current more heuristic rules of thumb such as those currently used in fisheries management to account for uncertainty.

@@

```{r sims, fig.width=7, fig.height=3.5, fig.cap="Average fish biomass under different management strategies under increasing levels of measurement uncertainty. Each plot the mean stock size over time across 100 replicate simulations under each policy: constant escapement (CE), Total allowable catch (TAC = 80% MSY), and the proposed partially observed Markov decision process (POMDP) method. Measurement error increases as a normal distribution with standard deviation 0, 0.1, or 0.15, as indicated at the top of the panel.  Environmental stochasticity is fixed a standard deviation of 0.15 in each panel.  Carrying capacity K normalized to 1, r = 0.75. Additional environmental noise levels and comparison to MSY rather than TAC can be found in the supplementary material. \\label{sims}"}
sims %>%
  select(-value) %>%
  filter(method != "msy", sigma_g == "0.15") %>%
  mutate(method = fct_recode(method, 
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  group_by(time, method, sigma_m) %>%
  summarise(mean = mean(state), sd = sd(state)) %>% 
  mutate(sigma_m = as.character(sigma_m)) %>%
  ungroup() ->
fig1_df

@@

```{r econ, fig.width=7, fig.height=3.5, fig.cap="Expected net present value of the fishery across strategies under increasing levels of measurement error $\\sigma_m$. Net present value is th sum of all future harvests discounted over time and averaged across 100 replicates simulations under each strategy, as shown in Figure \\ref{{sims}}. The value under constant escapement (CE) is optimal when measurements are perfect but decreases rapidly with increasing measurement error. The more cautious TAC is not economically optimal but largely unimpacted by increasing error, while POMDP attains consistently high economic yield despite the increasing uncertainty. \\label{econ}"}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g == "0.15", method != "msy") %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%
  mutate(method = fct_recode(method,
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%

@@

This pattern in management success in ecological terms (the relatively recovery and maintenance of fish biomass) is also bourne out in terms of economic performance.  Figure \ref{econ} shows the mean net present value (averaging across replicates and discounting future profits by the discount factor $\gamma$) for these same simulations at increasing levels of measurement uncertainty.  As before, environmental stochasticity is set at $\sigma_g = 0.15$.  In the absense of measurement uncertainty, constant escapement (CE) is optimal (as per @Reed1979), while the heuristic caution built into the total allowable catch (TAC) strategy (at 80% MSY) results in a sub-optimal economic yield.  The presense of stochasticity in recruitment ($\sigma_g = 0.15$), also contributes to the reduction in yield under TAC.  Though CE is quite robust to the environmental stochasticity level, this strategy proves very sensitive to increasing measurement error, showing sharp declines in economic value, falling below the TAC economic value at $\sigma_m = 0.15$.    Though the risk of stock collapse does increase with increasing measurement error under TAC (as seen by the mean declines in Figure \ref{sims}), these have little impact on the economic value due to the discount rate.  A smaller discount rate would penalize unlikely but not improbable collapses more, since a significant amount of time is required to realize those rare events.  Supplemental Figure S3 summarizes these economic trends across different noise values $\sigma_g$ and includes comparison to a simple MSY policy.  In contrast to the declining economic performance of CE and the consistently sub-optimal economic yield for TAC, the POMDP strategy continues to generate economic yields at approximately the optimal level (as attained by CE in the absense of measurement error) despite the increasingly uncertain measurements.  This demonstrates that the reduced risk of stock collapse and higher average stock biomass attained by the POMDP strategy in the presence of high measurement error, Figure \ref{sims}) is not the result of a trivial reduction in harvesting under all circumstances, but rather, evidence of a more nuanced strategy that manages to account for the uncertainty in measurement while maintaining a reasonable harvest.

@@

```{r overest, fig.width=4, fig.height=3.5, fig.cap = "Average fish biomass when the POMDP strategy assumes a high level of measurement uncertainty, while simulations reflect perfect measurements.  Despite this overestimation, biomass under POMDP strategy closely tracks the optimal biomass under CE in the absence of measurement error.  \\label{overest}"}
overest_sims %>%
  filter(method != "MSY") %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))  + 
  theme(legend.position = "bottom") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) 
```

The POMDP strategy is also robust to overestimation of the level of measurement uncertainty.  In the simulation results shown in Figures \ref{sims} and \ref{econ}, we have assumed that the level of measurement uncertainty $\sigma_m$ was known, and saw that ignoring this uncertainty (as the CE policy does) has significant negative impact on ecological and economic outcomes.  If the level of measurement uncertainty is not known precisely, _overestimating_ the measurement error while using the POMDP strategy provides a precautionary approach that can nevertheless achieve nearly optimal ecological and economic outcomes.  Figure \ref{overest} summarizes the results of the same simulations as before, but under the scenario in which the POMDP approach assumes a measurement error of $\sigma_m = 0.15$, when in fact all simulated measurements are made without error ($\sigma_m = 0$).  This represents an extreme case of ovestimating the measurement error. Stochastic growth remains the same as before, $\sigma_g = 0.15$, and simulations under TAC and CE policies are shown for comparison.  When measurement error is absent, Reed's proofs hold and the CE strategy is optimal. Figure \ref{overest} shows that the POMDP outcomes track almost exactly the CE outcomes despite the misplaced assumption that measurements are quite poor.  (As we have already seen, the TAC stategy is insufficiently cautious for this level of stochasticicty in recruitment, resulting in overexploitation and long-term decline). The ability of the POMDP solution to perform nearly optimally even when significantly overestimating the level of measurement uncertainty contrasts sharply to the significant declines from ignoring measurement uncertatinty seen in the CE solutions in Figure \ref{sims}.  This demonstrates that while we may not know precisely the level of measurement error, we achieve far better outcomes overestimating measurement uncertainty than underestimating it.  This also underscores the observation that POMDP policy is quite robust to the details of the uncertainty.  We can get a better understanding for the performance of POMDP in these simulations by looking more closely at how any individual decision under a POMDP strategy compares to the action chosen by the current alternatives.

```{r policy, fig.width=5, fig.height=6, fig.cap="Comparison of the harvest and escapement policies under each strategy as a function of the observed stock size.  Escapement refers to the expected fraction of fish left in the sea, $x-h$, while harvest refers to the target catch; two different conventions for plotting the same action. Uniquely, the POMDP policy plot will depend not only on the observed stock size, but also depends on prior information (bottom panel) as determined from any prior observations and actions.  Depending on this prior it may harvest less or more than the other policies given an identical observation.\\label{policy}", message=FALSE, warning=FALSE}
policies_w_priors %>% 
  gather(panel, value, -state, -policy) %>%
  rename(method = policy) %>%
  ggplot(aes(state, value, col=method)) + 
  geom_line(lwd=1)  +
  facet_wrap(~panel, ncol=1, scales = "free_y") +
  xlab("observed stock size") +
  ylab("policy") +
  scale_color_manual(values = colors) +
#  theme(legend.position = "bottom") +
  coord_cartesian(xlim = c(0,1), ylim = c(0,.8))

To better understand the differences in performance of these strategies and resolve the paradox of uncertainty, we must take a closer look at how the specific action recommended by each policy compares given the same observation.  Figure \ref{policy} shows the action taken by each strategy in response to a measurement of the stock size (biomass estimate).  These plots show, for any possible observations, which strategy will attempt to harvest most and which will attempt to harvest least.  The first panel shows the policy in terms of expected escapement, $S = Y - H$ for observed stock $Y$ and harvest $H$, consistent with most of the relevant control and bioeconomics literature [e.g. @Reed1979; @Clark1986; @Sethi2005].  For comparison, the second panel shows the same policies but in terms of harvest $H$.  These plots clearly illustrate the contrast between the constant escapement (CE) strategy and the precautionary Total Allowable Catch (TAC) strategy: CE sets harvest strictly to zero for stocks estimated at biomass below $B_{MSY}$, while TAC permits a modest harvest of even very small stocks.  Escapement CE strategy corresponds to keeping escapement constant.  This is important, as theoretical work ever since the proofs of @Reed1979 often attempts to simplify the calculations by assuming the optimal policy must be a constant-escapement type strategy [e.g. @Ludwig1981; @Roughgarden1996; @Engen1997;  @Moxnes2003].  Note that both CE and TAC policies are independent of the levels of uncertainty $\sigma_m$ and $\sigma_g$.  TAC implicitly accounts for some uncertainty through its 80% MSY definition -- comparable plots with MSY can be found in the Supplemental Material.  In principle, the CE policy could depend on $\sigma_g$, but as @Reed1979 proved, the constant escapement level with stochasticity is the same as in the deterministic case, S = D, unless the noise level is quite high (comparison plots in Supplemental material.)  In contrast to this, our POMDP plots depend very much on both the choice of $\sigma_m$ and $\sigma_g$.  If $\sigma_m = 0$, they reduce exactly to the CE solution.  Here we show the corresponding policies for POMDP solutions focusing on $\sigma_g = 0.15$ as above, with a modest measurement uncertainty $\sigma_m = 0.1$.  Alternate combinations of measurement uncertainty can be found in the appendix but do not change the general pattern.  In addition to an explicit dependence on the measurement error, our POMDP solutions depend on another piece of information: any prior observations of the stock size.

@@

So far we have focused on simulation and an examination of the relative policies under different prior information.  Figure \ref{historical} compares the harvest level that would have been recommmended by each of the strategies we have considered here against the historically observed catch recorded for two commericially fished stocks: Argentine Hake and European Plaice.  Historical estimates of biomass and catch are taken from the R.A. Myers Legacy Stock Assessment database [@RAM]. Posterior distributions for parameters for the Graham-Schaefer model are estimated with uncertainty through Markov Chain Monte Carlo using `nimble` [@nimble] on the historical data, illustrating how this process might be done in more complex models as well (details and code in Supplement, Appendix B).  $B_{MSY} and corresponding TAC and CE policies are calculated based on posterior mean estimates of the model parameters, along with POMDP solution assuming a 10% measurement error rate.  Though measurement error could be estimated directly from the raw data, this would not reflect the true measurement uncertainty arising from the stock assessment process.  Each strategy is then compared to historical observations to determine a recommended harvest.  As we have seen, the TAC and CE harvest policies are uniquely determined by the observed stock size relative to $B_{MSY}$, but the POMDP policy must be re-calculated each time step to reflect both the prior observation and prior action.  Note that since we cannot replay history under these alternative policies, so the prior action taken is always the historical catch for that year and not the catch recommended by the POMDP policy.

These historical examples provide another useful lens to compare how the different strategies respond in the face of fluctuations in real data, rather than model simulations.  In both stocks, historical catch almost always exceeds that recommended by any of our strategies, falling closer to the MSY value estimated (see appendix).   In Argentine Hake, the persistent declines result in both POMDP and CE strategies quicly closing down the fishery in an attempt to let the stock recover to a more productive target biomass, while TAC persists with merely a reduced harvest.  A small recovery of biomass in 1995 is met by an immediate uptick in harvest under CE, while the POMDP response is more conservative.  The example of European Plaice illustrates more volatility in the stock size, revealing further differences in the strategies.  Despite this volatility, the TAC level remains relatively level across all five decades, rising or dipping only slightly with changes in stock size.  In contrast, the CE harvest tracks this volatility almost in perfect mirror.  Here, the POMDP solution falls in between these extremes, almost mirroring which-ever of the two policies is more conservative: the POMDP solution matches the dips in harvest taken by CE to allow the stock to recover most quickly, but does not track the doubling of harvests recommended by CE in the mid 1980, increasingly only to the more modest harvest recommended by the TAC policy.   Once again, we see that POMDP solution provides a more consistently precautionary policy than either the over-simplified optimal control solution of CE or the more rule-of-thumb approach represented by TAC.  Though we have seen that the POMDP solution need not always be more conservative (lower harvest) than these strategies, it makes use of the all prior observations to tune the level of caution appropriately.

# Discussion
